|

### 2021-08-14 paper/dcpo_demsupport.Rmd
revise abstract, revise text up to #Results

title: "Democracy, Public Support, and Measurement Uncertainty"
thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."

@@

abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses. In this letter, we correctly take this uncertainty in account and show that there is no support for the conclusion of either study. We then work to minimize the measurement uncertainty in public support by bringing additional survey data and a superior model of public opinion. Even with these improvements, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty. [149/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, IRT."

@@

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

_It is worth to note that, despite the great effort of collecting data and identifying differences, we could not reach a completely primary replication of @Claassen2020a's Dataverse materials.
Specifically, we have five fewer observations, three of which are no longer available in original survey data and two seem to have never existed, and one more survey item which was conflated in original data.
(See more details in Online Supplementary Material \@ref(dgp).)
Nevertheless, given there are over 2000 observations involved in the analysis, the five missing should not make a meaningful difference._

@@

Although measurement uncertainty has yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254]. 
Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via a technique known as the "method of composition" (MOC) [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
See more details of the method and the operational process in Online Appendix C.

@@

As a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set,  assembling as much survey data on democratic support as possible. We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, 128, Model 1] in the left panel and democratic support separated by regime type (Model 2) on the right.
The uppermost set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty, and reproduce that article's findings.
The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
In both models, the positive coefficients for democratic support are no longer statistically significant.
The uppermost set of results replicate @Claassen2020a without uncertainty.
The middle results introduce the uncertainty in the measurement of public support and democracy indices into the model.
And the lowermost set presents the results estimated with the expanded data with uncertainty.

In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models or controlling for corruption alter the conclusion (see Online Supplementary Material \@ref(moc) for the the result of the full-pack analyses).

@@

# Data Recollection and Uncertainty in Control Variables {#dgp}

@@

# Appendix B: DCPO Replication {#dcpo}

@@

# Appendix C: The Method of Composition {#moc}

@@

# Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)

>>>>

title: |
  | Democracy, Public Support, 
  | and Measurement Uncertainty
# thanks: "The authors contributed equally to this work.  Corresponding author: [yuehu@mail.tsinghua.edu.cn](mailto:yuehu@mail.tsinghua.edu.cn).  Current version: `r format(Sys.time(), '%B %d, %Y')`."

@@

abstract: "Do democratic regimes depend on public support to avoid backsliding? Does public support, in turn, respond thermostatically to changes in democracy? Two prominent recent studies (Claassen 2020a, 2020b) reinvigorated the classic hypothesis on the positive relationship between public support for democracy and regime survival---and challenged its reciprocal counterpart---by using a latent variable approach to measure mass democratic support from cross-national survey data. But such approaches come with concomitant measurement uncertainty, and neither study incorporated this uncertainty into its analyses. In this letter, we correctly take measurement uncertainty in account and show that there is no support for the conclusion of either study. We then work to minimize the measurement uncertainty in public support by incorporating additional survey data. Even with this expanded evidentiary base, however, our analyses fail to yield evidence in support of either hypothesis, underscoring the necessity of accounting for measurement uncertainty. [144/150 words]"
keywords: "Democratization, public support, regime survival, measurement uncertainty, latent variables"

@@

We proceed in three steps.
First, we reproduce the original analyses of Claassen [-@Claassen2020a; -@Claassen2020b], which included only the point estimates of the latent variable of democratic support and so exclude its measurement uncertainty.
Second, we collect the original cross-national survey data, replicate the latent variable measure of democratic support used in the two articles, and conduct the articles' analyses again, this time maintaining the entire distribution of estimates of democratic support in each country-year.
As democracy is also a latent variable in these analyses, we include the uncertainty in its estimates as well, along with that for corruption in the second analysis of @Claassen2020b.
In the third step, we collect even more survey data---increasing these source data by one-third---and re-estimate the two articles' analyses once more, again maintaining the full distribution of estimates to preserve measurement uncertainty.

@@

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement uncertainty, and ignoring that uncertainty in analyses can both attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @Blackwell2017a, 360-361; @caughey2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254]. 
Following this line, after replicating the original analyses with point estimates, we incorporate uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via the technique known as the "method of composition" [@Tanner1993, 52; @Treier2008, 215; @caughey2018, A15-16].
See more details of the method and the operational process in the Supplementary Materials.

@@

To provide a further test of the classic arguments on democracy and public support, we generated estimates of democratic support using the same procedure as in Claassen [-@Claassen2020a; -@Claassen2020b] on a bigger data set, assembling as much survey data on democratic support as possible. We employed `r dcpo_input_ncyi` national opinions on democracy from `r dcpo_input_surv` national surveys, representing a `r increase_cyi`% and `r increase_surv`% increase respectively over the `r supdem_ncy` opinions and `r supdem_surv` national surveys used in Claassen [-@Claassen2020a; -@Claassen2020b].^[These figures represent the survey data actually used in estimating public support for democracy; as in Claassen [-@Claassen2020a; -@Claassen2020b], countries for which two separate years of survey data were not available were excluded.]

@@

Figure \@ref(fig:plot-mainAJPS) presents the reanalyses of the hypothesis that public support influences the level of democracy, with democratic support pooled for all countries [@Claassen2020a, 128, Model 1] in the left panel and democratic support separated by regime type (Model 2) on the right.
The uppermost set of results replicate the analysis of @Claassen2020a, including its exclusion of measurement uncertainty, and reproduce that article's findings.
The middle results introduce a single change: the uncertainty in the measurement of public support is taken into account.
<!-- In both models, the positive coefficients for democratic support are no longer statistically significant. -->
The bottom results also incorporate uncertainty but additionally replace the estimates of democratic support with those based on the expanded dataset; this change works to increase the number of observations analyzed as well.
<!-- Although the confidence intervals shrink considerably, the coefficient estimates move much closer to zero; the hypothesis remains unsupported.  -->

_In comparison to the original result, the positive coefficients for democratic support in both models accounting for the uncertainty are no longer statistically significant.
This result is robust when using separated regime types in the explanatory variable. 
Nor do applying system GMM models or controlling for corruption alter the conclusion (see the Supplementary Materials)._

@@

# Supplementary Appendix A: Data Recollection and Uncertainty in Control Variables {#dgp}

@@

# Supplementary Appendix B: DCPO Replication {#dcpo}

@@

# Supplementary Appendix C: The Method of Composition {#moc}

@@

# Supplementary Appendix D: Secondary Models from Claassen (2020$a$, 2020$b$)
